### 2018-08-01 CS761-RandomizedAlgorithms/assignments/a4.tex
q4

@@

>>>>

	I collaborated with Sharat, and discussed briefly with Harry and Logan.

@@

	Let $t \geq 0$. We want to show the existence of a vertex $v$ in $S$ such that $\sum_{i\in S} p^t(i) \geq 1- t\phi(S)$ when the random walk is started with $p_0 =\chi_v$. \emph{Note:} I'm not sure if I got the quantifiers backwards for this problem. Sorry if I did, I hope the ideas are still worth some merit in this case.
	Choose a vertex $u \in S$ uniformly at random to start the walk at. Then
	$$E[\chi_Sp^t] = \sum_{u \in S} \chi_SW^t\chi_u \cdot\frac{1}{|S|} = \frac{1}{|S|}\chi_SW^t\chi_S.$$
	Since $W^t = A^tD^{-t} = \frac{1}{d^t}A^t$, we thus have that
	$$E[\chi_Sp^t] = \frac{1}{d^t|S|}\sum_{u,v\in S}w_t(\{u\},\{v\}) = \frac{1}{d^t|S|}w(S,S)$$
	where we use $w_t(A,B)$ to denote the number of walks of length $t$ from any vertex in $A$ to any vertex in $B$ in $G$, for $A, B\subseteq V$.
	We want
	$$E[\chi_S p^t] \geq 1-t\phi(S)$$
	and so using the above equation for this expection it would suffice to show (after rearranging)
	$$w_t(S,S) \geq d^t|S| - td^{t-1}|\delta(S)|.$$
	Since $G$ is $d$-regular, a length $t$ walk starting in $S$ and ending at any vertex in $V$ is uniquely determined by $d$ choices of which vertex to branch to next, from each vertex in the walk. Thus $w_t(S,V) = d^t|S|$. Hence our desired inequality is equivalent to showing
	$$td^{t-1}|\delta(S)| \geq w_t(S,V) - w_t(S,S) = w_t(S,V\backslash S).$$
	But it is not hard to see that the Left Hand Side is a generous overcounting of $w_t(S,V\backslash S).$ Indeed, the expression $td^{t-1}|\delta(S)|$ counts the number of walks which start in $S$ and use an edge of $\delta(S)$ in at least one of their $t$ positions, then have free choice of any of $d$ edges for each of their remaining $t-1$ positions. Therefore the inequality
	$$td^{t-1}|\delta(S)| \geq w_t(S,V\backslash S)$$
	holds, and so the equivalent statement
	$$E[\chi_S p^t] \geq 1-t\phi(S)$$
	holds as well.
	Since we know $E[\chi_S p^t] \geq 1-t\phi(S)$ there must exist some vertex $v \in S$ for which $\chi_S p^t \geq 1-t\phi(S)$ when $p_0 = \chi_v$. For otherwise such an expectation could not be attained.$\blacksquare$
